\section{Embed 812}
\subsection{Personal Protective Equipment}\label{PPE}
Begin first by grabbing a lab coat and then use paper towels and acetone to
clean off the scale used for measuring out the mass of various resin mixtures.

\subsection{Recipe for EMbed 812}\label{EMbed_812}
Remove the four chemicals for the EMbed 812 resin from the cabinet by using the
WPE-147.  Where W.P.E. is the Weight per Epoxide Equivalent).

\begin{table}[h!]
	\centering
	\begin{tabular}{|c|c|}
		\hline
		{\bf Ingredient} & {\bf Unit}\\ \hline\hline
		EMbed 812 Resin & 51.80 g\\ \hline
		DDSA & 26.68 g\\ \hline
		NMA & 21.67 g\\ \hline
		BDMA & 2.5 ml\\ \hline
	\end{tabular}
    \caption{Simplified instructions to check and make sure the automatic
    tissue processor is set up at the correct stations.  Each vial should be
    filled with 20 ml when processing.  Be sure to check the program on the
    automatic tissue processor; it should be marked by program \#2.}
\end{table}

\section{Lab Equipment}\label{lab_equipment}
Grab one (400 ml) Tripore container along with four clean pipettes.

\section{EMbed 812}\label{EMbed_812_Resin}
Balance the scale with the Tripore container and pour in 51.80 g of EMbed 812
Resin.  Clean the bottle and cap with Kimwipes and throw out the pipette.  Grab
a strip of Parafilm to stretch over the cap to ensure an air-tight seal. 

\section{DDSA}\label{DDSA}
Balance the scale after 51.80 g of EMbed 812 Resin has been added to the
Tripore container.  Add 26.68 g of DDSA to the container by first underpouring
and then using a pipette to add the rest of the DDSA.  Clean the bottle and cap
with Kimwipes and throw out the pipette.  Grab a strip of Parafilm to stretch
over the cap to ensure an air-tight seal. 

\section{NMA}\label{NMA}
Balance the scale after 26.68 g of DDSA has been added to the Tripore
container.  Add 21.67 g of NMA to the container by first underpouring and then
using a pipette to add the rest of the NMA.  Clean the bottle and cap with
Kimwipes and throw out the pipette.  Grab a strip of Parafilm to stretch over
the cap to ensure an air-tight seal. 

\section{Stir}
Move the Tripore container inside the hood.  Add a stirbar to the Tripore
container containing EMbed 812 Resin, DDSA, and NMA to stir the mixture for 10
minutes in the hood.

\section{BDMA}
In the hood, while the Tripore container is being stirred, use a graduated
micropipette and obtain 2.5 ml of BDMA.  The BDMA is used as the accelerant for
polymerization.  

\section{Stir}
Stir the Tripore container containing EMbed 812 Resin, DDSA, NMA, and BDMA
mixture for 10 minutes in the hood.  The mixture should turn orange after the
BDMA has been added.

\section{Parafilm}
Using Parafilm wrap, ensure that each chemical lid has been wrapped to keep an
air-tight seal.

\section{Syringe}
Grab eight syringes and caps from the cupboards and prepare them for filling up
with the resin.  Place the newly filled resin syringes in the freezer.  

\section{Clean-up}
Clean the magnetic stirbars with acetone.  Be sure to put vinyl liners inside
the gloves.

\section{Embed}
Embed the tissue samples!
